---
title: "Alcohol vs Seat choice"
author: "Christina Jilavdaryan"
date: "9-17-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in?

$H_0$ There is no difference in alcohol consumption based on where one sits in class.

$H_A$ There is a difference in alcohol consumption based on where one sits in class.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
 
 
The boxplot shows that people who drink more alcohol on average tend to sit in the back, while the people in the front or in the middle seats of the class tend to show less of a difference in drinking patterns.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This fancy box plot shows the significant difference between the alcohol consumption of the back row and the middle row, along with showing the difference between the back row and the front row's alcohol consumption.



## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```



Based on this chart, the back row has 8.5 more than the middle or front rows per week. The middle row is shown to drink 3.3 drinks per week and the front row has 1.7 drinks per week. However it's likely that the amount of drinks each row has is not the same so the quantity in each persons drink may differ. 



## Inferential Tests




```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

This inferential test shows that the p-value is 0.000116, and this value shows the chances of getting the same results as the ones found in this study if the null hypothesis is actually true. Because the p-value is so small I will reject the null hypothesis.

## Conclusions


