---
title: "Alcohol vs Seat choice"
author: "Christina Jilavdaryan"
date: "9-17-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in?

$H_0$ There is no difference in alcohol consumption based on where one sits in class.

$H_A$ There is a difference in alcohol consumption based on where one sits in class.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
 
 
The boxplot shows that people who drink more alcohol on average tend to sit in the back, while the people in the front or in the middle seats of the class tend to show less of a difference in drinking patterns.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


